\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}

### 2023-12-02 text/proposta/prop.tex
logbook 1

>>>>

We expect to obtain the energy spectrum of the alpha particles resulting from the reaction between the protons and the samples. 
For the glass samples, we expect to see a profile due to the particles that come from different depths of the sample and therefore have lost different amounts of energy. In the implant samples, we expect to see a peak at the energy corresponding to the energy of the alpha particles produced by the reaction.
In both cases, the samples is composed by other types of atoms such as silicon and boron, which will also emit charged particles.

Other phenomena such as Rutherford Backscattering and Elastic Scattering are also expected to occur.
